---
title: "Abridge AI Scribe in OTO"
author: "JP Giliberto and Jen Ren"
format: html
---

## Wrangle
### Load Packages

```{r}
#| echo: false
#| message: false
#| warning: false
#| results: "hide"
#| code-fold: true

#loading standard packages for data wrangle and visualization. JPG just commented out packages I don't think we will use. 
library (tidyverse)
library(readr)
library (lubridate)
library(readxl)
library(forcats)
library(scales)
library(ggthemes)
library(ggrepel)
library(janitor)
library(gt)
#library(ggridges)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(fuzzyjoin)
#library(ggsignif)

```

### Load DeID data

```{r}
#| echo: false
#| message: false
#| warning: false
#| results: "hide"
#| code-fold: true


ExStudyIDs <- c("ID563", "ID760", "ID871")

# Sessions are number of abridge activations
SessionsRaw <- read_csv("Raw Data DeID/Abridge Sessions 09 25 to 01 31.csv") |> 
  select(2:4)

#signal data raw with dates
SignalRaw1 <- read_csv("Raw Data DeID/Signal Data 12 22 to 01 26.csv") |> 
  select(StartDate = `Reporting Period Start Date`, EndDate = `Reporting Period End Date`, 4:9) |> 
  mutate(GroupData = case_when(StudyID == "ID928" & StartDate >"2025-02-01" ~ "AIScribe",
                               StudyID == "ID928" & StartDate <"2025-01-01" ~ "Control",
                               StudyID == "ID928"  ~ "Transition",
                               StartDate > "2025-9-01"~ "AIScribe",
                               StartDate < "2025-08-15" ~"Control",
                               T ~"Transition")
 
                       ) |> 
  filter(!StudyID%in%ExStudyIDs)

#eliminate months where the provider did not see more than a threshold (at least 20). 25 of 778 (3.2%) provider months eliminated
KeyApptsPerMo <- SignalRaw1 |> 
  filter(Metric == "Appointments per Day") |> 
  select(StudyID, StartDate,Numerator) |> 
  mutate(ThresholdAppt = Numerator >19) |>  
  #count(ThresholdAppt) |> 
  select(-Numerator)

SignalRaw <- SignalRaw1 |> 
  left_join(KeyApptsPerMo) |> 
  filter(ThresholdAppt) |> 
  select(-ThresholdAppt)

Groupdata_lvl <- c("Control", "Transition", "AIScribe"  )

SignalRaw$GroupData <- factor(SignalRaw$GroupData, levels = Groupdata_lvl )

SurveyRaw <- read_csv("Raw Data DeID/Survey - Baseline.csv") |> 
  select(2:57)

VisitsRaw <- read_csv("Raw Data DeID/visits data 12 1 2022 to 01 31.csv") |> 
  select(VisitType = `Visit Type`, Date = `Visit Date`, LOS = `Level of Service`, StudyID) |> 
  filter(LOS !="ERROR") |> 
  filter(!str_detect(VisitType, "SUPPORT")) |> 
  mutate(VisitCat = case_when(str_detect(VisitType,"NEW")~ "NEW",
                             str_detect(VisitType,"TELE")~ "TELEMED",
                             str_detect(LOS, "9924")~ "TELEMED",
                             str_detect(LOS, "99241")~ "TELEMED",
                             str_detect(LOS, "9921")~ "RETURN",
                             str_detect(LOS, "99024")~ "OTHER",
                             str_detect(LOS,  "PROC")~ "OTHER",
                             #str_detect(VisitType,  "PROCEDURE")~ "OTHER",
                             str_detect(LOS,  "NOCH")~ "OTHER",
                             str_detect(LOS, "99203")~ "NEW",
                             str_detect(LOS, "99204")~ "NEW",
                             str_detect(LOS, "99205")~ "NEW",
                             str_detect(VisitType, "BOTOX")~"OTHER",
                             T~"RETURN")) |> #what was left was 99202 in a return slot
  group_by(StudyID, Date,VisitCat) |> 
  summarise(n= n()) |> 
  pivot_wider(names_from = VisitCat, values_from = n)

VisitsRaw$Date <- ymd( VisitsRaw$Date, tz = "UTC")

```

### Create or Load Keys
```{r}
#| echo: false
#| message: false
#| warning: false
#| results: "hide"
#| code-fold: true

KeyIDRole <- read_csv("Participant Key ID.csv") |> 
  select(2:3)

KeyPercentAmbient <- SignalRaw |> 
  filter(str_detect(Metric, "mbient")) |> 
  select(StudyID, StartDate,PercentAmbient = Value)

#High vs Low Users. we can discuss best way to do that. median 106
SubKeyTotalAbridgeSessions <- SessionsRaw |> 
   filter(!StudyID%in%ExStudyIDs) |> 
   group_by(StudyID) |> 
   summarise(n = sum(`Abridge Sessions`, na.rm = T)) 

SubKeyTotalVisitsNewRet <-VisitsRaw |>
  filter(!is.na(StudyID)) |> 
  filter((StudyID == "ID928" & Date >"2025-09-01")|
          (StudyID != "ID928" & Date >"2025-09-01" )) |> 
  group_by(StudyID) |> 
  summarise(NewRet = sum(NEW+RETURN, na.rm = T))
  

KeyUserHigh <- SubKeyTotalAbridgeSessions |> 
  left_join(SubKeyTotalVisitsNewRet) |> 
  mutate(ProportionAbridge = case_when(n/NewRet > 1 ~100, 
                                       T ~ round(n/NewRet,2)*100) )|> 
  mutate(HighUser = ProportionAbridge > 70 ) |> 
  #60 would be half. 180 is N median
  select(1,4:5)
  
KeyDenominator<- SignalRaw |> 
  select(StudyID,StartDate, EndDate,Metric, Numerator, Denominator) |>
  mutate(DenomUnits = case_when(str_detect(Metric, "Time in Notes per Appointment") ~ "per Appointment",
                                 str_detect(Metric, "Time in System per Day") ~ "per Day with a Login",
                                 str_detect(Metric, "Time On Unscheduled Days") ~ "per Unscheduled Day",
                                str_detect(Metric, "Appointments per Day") ~ "per Scheduled Day",
                                 T ~ NA)) |> 
  filter(!is.na(DenomUnits)) |> 
  group_by(StudyID,StartDate, EndDate, DenomUnits) |> 
  summarise(denom_max = max(Denominator, na.rm = T)) |> 
  pivot_wider(names_from = DenomUnits,values_from = denom_max)



BaselineMeans <- SignalRaw |> 
  filter(GroupData=="Control") |> 
  group_by(Metric, StudyID) |> 
  summarize(Count = n(),
            BaselineMean = mean(Value, na.rm = T))

BaselineNotesPerAppt <- BaselineMeans |> 
  filter(Metric =="Time in Notes per Appointment")
 
```

##WOWH PJTime and Unscheduled Days
**APPs need to be exclude from anything that has time on unscheduled days as they are often scribing for other attendings on unscheduled Days

### WOWH total reduction - High Users

```{r}
#| message: false
#| warning: false
#| code-fold: true

APP <- c("ID563","ID606","ID888","ID006")

LMWOWHData <- SignalRaw |>
  filter(Metric == "Pajama Time" | Metric == "Time On Unscheduled Days")|>
  filter(GroupData !="Transition") |>
  filter(!StudyID %in% APP)|> 
  group_by(StudyID,StartDate,GroupData) |> 
  summarise(WOWHmontly = sum(Numerator,na.rm =T)) |> 
  left_join(KeyDenominator, join_by(StudyID,StartDate)) |> 
  left_join(KeyUserHigh) |> 
  filter(HighUser) |> 
  mutate(HrsPerDay = WOWHmontly/`per Appointment`/60*20) |> 
  select(StudyID, WOWHmontly, GroupData, HrsPerDay)

LMWOWH <- lmer(formula = HrsPerDay ~ (GroupData) + (1|StudyID), data = LMWOWHData)

 LMWOWHcoef <- tidy(LMWOWH, effects = "fixed") |> 
  gt()
 LMWOWHcoef |> 
       data_color(columns = p.value,
              method = "bin",
               palette = c("green","yellow","red"),
               bins= c(1.0,0.15,0.05,0))
 
```

### WOWH Pajama Time, High Users

```{r}
#| message: false
#| warning: false
#| code-fold: true

LMPJData <- SignalRaw |>
  filter(Metric == "Pajama Time")|>
  filter(GroupData !="Transition") |>
  group_by(StudyID,StartDate,GroupData) |> 
  summarise(PJmontly = sum(Numerator,na.rm =T)) |> 
  left_join(KeyDenominator, join_by(StudyID,StartDate)) |>
  left_join(KeyUserHigh) |> 
  filter(HighUser) |> 
  mutate(HrsPerDay = PJmontly*20/`per Appointment`/60) |> 
  select(StudyID, PJmontly, GroupData, HrsPerDay)

LMPJ <- lmer(formula = HrsPerDay ~ (GroupData) + (1|StudyID), data = LMPJData)

 LMPJcoef <- tidy(LMPJ, effects = "fixed") |> 
  gt()
 LMPJcoef |> 
    data_color(columns = p.value,
          method = "bin",
          palette = c("green","yellow","red"),
           bins= c(1.0,0.15,0.05,0))

 
```

### WOWH Unscheduled Day 

```{r}
#| message: false
#| warning: false
#| code-fold: true


APP <- c("ID563","ID606","ID888","ID006")

LMunSchData <- SignalRaw |>
  filter(Metric == "Time On Unscheduled Days")|>
  filter(GroupData !="Transition") |>
  filter(StudyID %in% APP)|> 
  group_by(StudyID,StartDate,GroupData) |> 
  summarise(Unsch = sum(Numerator,na.rm =T)) |> 
   left_join(KeyDenominator, join_by(StudyID,StartDate)) |> 
# left_join(KeyUserHigh) |> 
 # filter(HighUser) |> 
  mutate(HrsPerDay = Unsch*20/`per Appointment`/60) |> 
  select(StudyID, Unsch, GroupData, HrsPerDay)

LMunSch <- lmer(formula = HrsPerDay ~ (GroupData) + (1|StudyID), data = LMunSchData)

 LMunSchcoef <- tidy(LMunSch, effects = "fixed") |> 
  gt()
 LMunSchcoef |> 
          data_color(columns = p.value,
              method = "bin",
               palette = c("green","yellow","red"),
               bins= c(1.0,0.15,0.05,0))
```

## Time in Activity

### Time in Notes
```{r}
#| message: false
#| warning: false
#| code-fold: true

LMAllNotes <- SignalRaw |>
  filter(Metric == "Time in Notes per Appointment") |>
  filter(GroupData !="Transition") |> 
  select(StudyID, Value, GroupData, Denominator) |> 
  mutate(ValueD = Value *20/60)

#a models will be for time per appointment (mins)
#d models will be for time per typical full clinic day (hours)

LMNotesAppa <- lmer(formula = Value ~ (GroupData) + (1|StudyID), data=LMAllNotes)

summary(LMNotesAppa)
LMNotescoefa <- tidy(LMNotesAppa, effects = "fixed") |>
  mutate(Units = "Minutes Per Appointment")

LMNotesAppd <- lmer(formula = ValueD ~ (GroupData) + (1|StudyID), data=LMAllNotes)

summary(LMNotesAppd)
LMNotescoefd <- tidy(LMNotesAppd, effects = "fixed") |>
  mutate(Units = "hrs per typical day")
 
 LMNotescoef <- rbind(LMNotescoefd,LMNotescoefa) |> 
   mutate(EHRActivity = "Notes")
 
 LMNotescoef |> 
   gt() |> 
          data_color(columns = p.value,
              method = "bin",
               palette = c("green","yellow","red"),
               bins= c(1.0,0.15,0.05,0))
```
### Time in Clinical Review
```{r}
#| message: false
#| warning: false
#| code-fold: true

LMAllCR <- SignalRaw |>
  filter(Metric == "Time in Clinical Review per Appointment") |>
  filter(GroupData !="Transition") |> 
  select(StudyID, Value, GroupData, Denominator) |> 
  mutate(ValueD = Value *20/60)

#a models will be for time per appointment (mins)
#d models will be for time per typical full clinic day (hours)

LMCRAppa <- lmer(formula = Value ~ (GroupData) + (1|StudyID), data=LMAllCR)
LMCRcoefa <- tidy(LMCRAppa, effects = "fixed") |> 
  mutate(Units = "Minutes per Appointment")

LMCRAppd <- lmer(formula = ValueD ~ (GroupData) + (1|StudyID), data=LMAllCR)
LMCRcoefd <- tidy(LMCRAppd, effects = "fixed") |> 
  mutate(Units = "Hours per Typical Day")
                   
 LMCRcoef <-  rbind(LMCRcoefd, LMCRcoefa) |>
   mutate(EHRActivity = "Chart Review")

  LMCRcoef |>  
   gt() |> 
          data_color(columns = p.value,
              method = "bin",
               palette = c("green","yellow","red"),
               bins= c(1.0,0.15,0.05,0))
 


```
### Time in Orders
```{r}
#| message: false
#| warning: false
#| code-fold: true

LMAllOrders <- SignalRaw |>
  filter(Metric == "Time in Orders per Appointment") |>
  filter(GroupData !="Transition") |> 
  select(StudyID, Value, GroupData, Denominator) |> 
  mutate(ValueD = Value *20/60)

#a models will be for time per appointment (mins)
#d models will be for time per typical full clinic day (hours)

LMOrdersAppa <- lmer(formula = Value ~ (GroupData) + (1|StudyID), data=LMAllOrders)
LMOrderscoefa <- tidy(LMOrdersAppa, effects = "fixed") |>
  mutate(Units = "Minutes per Appointment")

LMOrdersAppd <- lmer(formula = ValueD ~ (GroupData) + (1|StudyID), data=LMAllOrders)
LMOrderscoefd <- tidy(LMOrdersAppd, effects = "fixed") |>
  mutate(Units = "Hours per Typical Full Clinic Day")

LMOrderscoef <- rbind(LMOrderscoefd, LMOrderscoefa) |>
   mutate(EHRActivity = "Orders")

LMOrderscoef|> 
  gt() |> 
          data_color(columns = p.value,
              method = "bin",
               palette = c("green","yellow","red"),
               bins= c(1.0,0.15,0.05,0))


```


### Time in In Basket
```{r}
#| message: false
#| warning: false
#| code-fold: true

LMAllIB <- SignalRaw |>
  filter(Metric == "Time in In Basket per Appointment") |>
  filter(GroupData !="Transition") |> 
  select(StudyID, Value, GroupData, Denominator) |>   
  mutate(ValueD = Value *20/60)

#a models will be for time per appointment (mins)
#d models will be for time per typical full clinic day (hours)

LMIBAppa <- lmer(formula = Value ~ (GroupData) + (1|StudyID), data=LMAllIB)

LMIBcoefa <- tidy(LMIBAppa, effects = "fixed") |>
  mutate(Units = "Minutes Per Appointment")

LMIBAppd <- lmer(formula = ValueD ~ (GroupData) + (1|StudyID), data=LMAllIB)

LMIBcoefd <- tidy(LMIBAppd, effects = "fixed") |>
  mutate(Units = "Hours per Typical Full Clinic Day")


 LMIBcoef <- rbind(LMIBcoefd, LMIBcoefa)|>
   mutate(EHRActivity = "In Basket")

 LMIBcoef |>
   gt() |> 
          data_color(columns = p.value,
              method = "bin",
               palette = c("green","yellow","red"),
               bins= c(1.0,0.15,0.05,0))
 LMIBcoef
```

##Publication Table - Changes in Time Acivity Table both Appt and typical full day

```{r}
#Need to run all of the Time in Activity code chunnks

 DataActAll<- rbind(LMCRcoef, LMNotescoef, LMIBcoef, LMOrderscoef) |> 
  mutate(Group = if_else(str_detect(term, "ribe"),"With AI Scribe", "Baseline"),
         Value = round(estimate,2),
         UCL = round((estimate+2*std.error), 2),
         LCL = round((estimate-2*std.error), 2),
         pValue = round (p.value, 4) 
         ) |> 
  select(Units:pValue) 


Results_SignalChanges <- DataActAll|> 
  mutate(AIScribeDelta = str_c(
    as.character(Value),
    " (",
    as.character(LCL),
    ", ",
    as.character(UCL),
    ") p value = ",
    as.character(pValue))) |>
  select(EHRActivity,Group,AIScribeDelta,Units) |> 
  pivot_wider(names_from = Group,values_from = AIScribeDelta) |> 
  mutate(Baseline = str_sub(Baseline,start = 1L,end = 4L))


```


## Time in Notes by TYPE of Visit
### Model - Just not enough data points in AI Scribe
```{r}
#| message: false
#| warning: false
#| code-fold: true

TimeInNotesAll <- SignalRaw |>
  filter(Metric == "Time in Notes per Appointment") |> 
  select(-Metric)

VisitsPerMo1 <- VisitsRaw |> 
  mutate(StartDate = case_when( Date <= "2022-12-31"~"2022-11-27",
                                Date <= "2023-01-28"~"2023-01-01",
                                Date <= "2023-02-25"~"2023-01-29",
                                Date <= "2023-03-25"~"2023-02-26",
                                Date <= "2023-04-29"~"2023-03-26",
                                Date <= "2023-05-27"~"2023-04-30",
                                Date <= "2023-06-24"~"2023-05-28",
                                Date <= "2023-07-29"~"2023-06-25",
                                Date <= "2023-08-26"~"2023-07-30",
                                Date <= "2023-09-30"~"2023-08-27",
                                Date <= "2023-10-28"~"2023-10-01",
                                Date <= "2023-11-25"~"2023-10-29",
                                Date <= "2023-12-30"~"2023-11-26",
                                Date <= "2024-01-27"~"2023-12-31",
                                Date <= "2024-02-24"~"2024-01-28",
                                Date <= "2024-03-30"~"2024-02-25",
                                Date <= "2024-04-27"~"2024-03-31",
                                Date <= "2024-05-25"~"2024-04-28",
                                Date <= "2024-06-29"~"2024-05-26",
                                Date <= "2024-07-27"~"2024-06-30",
                                Date <= "2024-08-31"~"2024-07-28",
                                Date <= "2024-09-28"~"2024-09-01",
                                Date <= "2024-10-26"~"2024-09-29",
                                Date <= "2024-11-30"~"2024-10-27",
                                Date <= "2024-12-28"~"2024-12-01",
                                Date <= "2025-01-25"~"2024-12-29",
                                Date <= "2025-02-22"~"2025-01-26",
                                Date <= "2025-03-29"~"2025-02-23",
                                Date <= "2025-04-26"~"2025-03-30",
                                Date <= "2025-05-31"~"2025-04-27",
                                Date <= "2025-06-28"~"2025-06-01",
                                Date <= "2025-07-26"~"2025-06-29",
                                Date <= "2025-08-30"~"2025-07-27",
                                Date <= "2025-09-27"~"2025-08-31",
                                Date <= "2025-10-25"~"2025-09-28",
                                Date <= "2025-11-29"~"2025-10-26",
                                Date <= "2025-12-27"~"2025-11-30",
                                Date <= "2026-01-31"~"2025-12-28", 
                                T~NA))



VisitsPerMo <-  VisitsPerMo1 |> 
  group_by(StudyID,StartDate) |> 
  summarise(New = sum(NEW, na.rm =T),
            #Return did not differ from telemed so we combine them
            Return = sum(RETURN,TELEMED, na.rm =T),
            Other = sum(OTHER, na.rm = T),
            Total = sum(NEW, RETURN, OTHER, TELEMED, na.rm = T)) |> 
  filter(Total>19) |> 
  filter(!is.na(StartDate))

VisitsPerMo$StartDate <- ymd(VisitsPerMo$StartDate, tz = "UTC")


TimeInNotesLM <- TimeInNotesAll |> 
  left_join(VisitsPerMo,join_by(StudyID, StartDate)) |> 
  left_join(KeyUserHigh)


NotesData4LMEM = TimeInNotesLM |> 
  filter(GroupData != "Transition") |> 
  filter(HighUser)

NotesData4LMEM$StudyID <- as_factor(NotesData4LMEM$StudyID)

NotesControlLMEM <- lmer(formula = Numerator ~ (New)*(GroupData) + (Return)*GroupData + (Other)*GroupData + (1|StudyID), data=NotesData4LMEM)


summary(NotesControlLMEM)				


```

## High Likelihood of 90% same day closure in High users\
```{r}
#| echo: false
#| message: false
#| warning: false
#| results: "hide"
#| code-fold: true

SamedayClosureRate <- SignalRaw |> 
  filter(Metric =="Percent of Appointments Closed Same Day") |> 
  filter(GroupData != "Transition") |>
  left_join(KeyUserHigh) |>
  filter(HighUser) |> 
  mutate(ClosureRate90 = Value>0.90)

ClosureGLM <- glm(ClosureRate90 ~ GroupData, family = binomial,data = SamedayClosureRate)
resultsClosure<- cbind( Category = "Closure > 90", tidy(ClosureGLM), confint.lm(ClosureGLM)) |> 
  mutate(OR = exp(estimate),
         LCL = exp(`2.5 %`),
         UCL = exp(`97.5 %`)) |> 
  select(1:2,9:11,6)
resultsClosure <- resultsClosure %>%
   mutate(
    across(
      where(is.numeric) & !all_of("p.value"),
      ~ round(.x, 2)) )

resultsClosure |> 
  gt() |> 
          data_color(columns = p.value,
              method = "bin",
               palette = c("green","yellow","red"),
               bins= c(1.0,0.15,0.05,0))
```

## Figures Normalized

### PJ Time

```{r}

#| echo: false
#| message: false
#| warning: false
#| code-fold: true
#need to run PJ wowh

GraphPJData <- SignalRaw |>
  filter(Metric == "Pajama Time")|>
  filter(GroupData !="Transition") |>
  group_by(StudyID,StartDate,GroupData) |> 
  summarise(PJmontly = sum(Numerator,na.rm =T)) |> 
  left_join(KeyDenominator, join_by(StudyID,StartDate)) |>
  mutate(HrsPerDay = PJmontly*20/`per Appointment`/60) |> 
  select(StudyID, PJmontly, GroupData, HrsPerDay)

BaselinePJDay <- GraphPJData |>
  filter(GroupData == "Control") |> 
  group_by(StudyID) |> 
  summarise(BasePJ = mean(HrsPerDay,na.rm =T))

TransitionDates <- SignalRaw |>
  filter(Metric == "Pajama Time")|>
  filter(GroupData =="Transition") |>
  select(StudyID,TransDate =StartDate)

NormalizedData <- GraphPJData |> 
  left_join(TransitionDates) |> 
  left_join(BaselinePJDay) |> 
  left_join(KeyUserHigh) |>
  mutate(NormPjHrsDay = HrsPerDay/BasePJ,
         DaysSinceTrans = as.double(StartDate-TransDate)) |> 
  group_by(HighUser,GroupData, DaysSinceTrans) |> 
  summarise(MeanNormPjHrsDay = mean(NormPjHrsDay)) |> 
  filter(GroupData !=   "Transition" )
         
  
ggplot(NormalizedData, aes(DaysSinceTrans, MeanNormPjHrsDay, group = HighUser, color = HighUser))+
  geom_smooth(se = F)+
  facet_wrap(vars(GroupData),   scales = "free_x")+
  geom_hline(yintercept = 1.0,linetype =2)+
    scale_y_continuous(
    labels = percent_format()
  ) +
   scale_color_manual(
    values = c( "wheat3", "purple3"))+
  theme_bw()

```

### Notes

```{r}

#| echo: false
#| message: false
#| warning: false
#| code-fold: true
#need to run PJ Wowh

GraphNotesData <- SignalRaw |>
  filter(Metric == "Time in Notes per Day")|>
  filter(GroupData !="Transition") |>
  group_by(StudyID,StartDate,GroupData) |> 
  summarise(Notesmontly = sum(Numerator,na.rm =T)) |> 
  left_join(KeyDenominator, join_by(StudyID,StartDate)) |>
  mutate(HrsPerDay = Notesmontly*20/`per Appointment`/60) |> 
  select(StudyID, Notesmontly, GroupData, HrsPerDay)

BaselineNotesDay <- GraphNotesData |>
  filter(GroupData == "Control") |> 
  group_by(StudyID) |> 
  summarise(BaseNotes = mean(HrsPerDay,na.rm =T))

TransitionDates <- SignalRaw |>
  filter(Metric == "Pajama Time")|>
  filter(GroupData =="Transition") |>
  select(StudyID,TransDate =StartDate)

NormalizedDataN <- GraphNotesData |> 
  left_join(TransitionDates) |> 
  left_join(BaselineNotesDay) |> 
  left_join(KeyUserHigh) |>
  mutate(NormNotesHrsDay = HrsPerDay/BaseNotes,
         DaysSinceTrans = as.double(StartDate-TransDate)) |> 
  group_by(HighUser,GroupData, DaysSinceTrans) |> 
  summarise(MeanNormNotesHrsDay = mean(NormNotesHrsDay)) |> 
  filter(GroupData !=   "Transition" )
         
  
ggplot(NormalizedDataN, aes(DaysSinceTrans, MeanNormNotesHrsDay, group = HighUser, color = HighUser))+
  geom_smooth(se = F)+
  facet_wrap(vars(GroupData),   scales = "free_x")+
  geom_hline(yintercept = 1.0,linetype =2)+
    scale_y_continuous(
    labels = percent_format()
  ) +
   scale_color_manual(
    values = c( "wheat3", "purple3"))+
  theme_bw()

```


